\section{Research Experience}

\outerlist{

\entrybig
	{\textbf{Graduate Student, Trottier Space Institute}}{September 2023 - Present}{Supervisor: Dr. Vicky Kaspi}{}

\emph{1. The Second CHIME/FRB Catalog}
\innerlist{
    \entry{Used the workflow framework to perform flux/fluence and sensitivity threshold calculations on 4500 events in CHIME/FRB Catalog 2.}
    \entry{Led the efforts to validate the results and perform relevant analysis to understand fluence distribution and assess biases in calculation.}
 }

\emph{2. Sensitivity Threshold estimates for CHIME/FRB system}
\innerlist{
    \entry{Integrated new plotting features for robust validation to ensure correctness and stability of the sensitivity threshold pipeline.}
    \entry{Created comprehensive user-focused documentation to support wide adoption within the CHIME/FRB collaboration.}
    \entry{Adapted the pipeline for compatibility with the workflow system, a bookkeeping framework for CHIME/FRB operations.}
    \entry{Extended the script to support raw voltage (baseband) data and VLBI localizations.}
    \entry{The pipeline is now widely used by CHIME/FRB collaborators and underpins several ongoing analyses of telescope sensitivity and burst detectability.}
 }

\emph{3. CHIME/FRB Catalog 2 Flux/Fluence Calculations}
\innerlist{
    \entry{Ported the pipeline to be compatible with the workflow system, using GitHub Actions to refactor the scripts, fix bugs, and update dependencies.}
    \entry{Set up collaboration-facing Docker environments to enable accessible functionality for running the pipeline.}
}

\entrybig
  {\textbf{Summer Intern, Trottier Institute for Research on Exoplanets}}{May 2023 – Aug 2023}
  {Supervisor: Dr. Jonathan Gagn\'e}{}

\emph{Planemos and Planet Formation}
\innerlist{
  \entry{Cross-matched NASA exoplanet data with the MOCA database to estimate system ages for young stellar populations.}
  \entry{Used KDEpy and Normalizing Flows to constrain exoplanet population distributions from sparse infrared data.}
  \entry{Developed an MCMC pipeline to calculate proper motions and parallaxes using multi-epoch WISE and Pan-STARRS data.}
}

\entrybig
  {\textbf{Undergraduate Thesis, McMaster University}}{Sept 2022 – Apr 2023}
  {Supervisor: Dr. Christine Wilson}{}

\emph{CO Isotopologues in Merging Galaxies}
\innerlist{
  \entry{Analyzed ALMA 3D data cubes to extract CO isotopologue line ratios in Antennae galaxies.}
  \entry{Studied optical depth and dust-to-gas ratio variations at different resolutions to trace ISM structure in mergers.}
}

\entrybig
  {\textbf{Independent Study Project, McMaster University}}{Sept 2022 – Dec 2022}
  {Supervisor: Dr. Sergey Sibiryakov}{}

\emph{Numerically Computing Fast Oscillating Integrals}
\innerlist{
  \entry{Developed C++ solvers for fast oscillating integrals using asymptotic expansions and Picard-Lefschetz theory.}
  \entry{Improved convergence performance of existing solvers for physics applications in lensing and wave optics.}
}

\entrybig
  {\textbf{Research Assistant, McMaster University}}{May 2022 – Aug 2022}
  {Supervisor: Dr. Laura Parker}{}

\emph{Phase Space Study of Star Formation in Cluster Galaxies}
\innerlist{
  \entry{Cross-matched SDSS with GALEX and MPA-JHU catalogs to study star formation via phase-space analysis of 100,000 galaxies.}
  \entry{Studied how environmental conditions suppress star formation in low-redshift galaxy clusters.}
}

\entrybig
  {\textbf{Research Assistant, McMaster University}}{Sept 2021 – Apr 2022}
  {Supervisor: Dr. Rob Cockcroft}{}

\emph{Developing a Two-Eyed Seeing Astronomy Course}
\innerlist{
  \entry{Helped design ASTRON 2A03 course integrating Indigenous astronomy with Western physics pedagogy.}
  \entry{Updated lecture materials, redesigned assessments, and built Planetarium-based experiential components.}
  \entry{Course supported EDI awareness and reconciliation through astronomy education.}
}

}